%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/VMReyes}{\Large Victor M. Reyes Espinoza}} & Email : \href{mailto:vmreyes@mit.edu}{vmreyes@mit.edu}\\
  \href{https://github.com/VMReyes}{https://github.com/VMReyes} & Mobile : +1-213-291-5378 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Massachusetts Institute of Technology}{Cambridge, MA}
      {Bachelor of Science in Computer Science and Engineering, Legal Studies, GPA: 4.6}{Aug. 2017 -- Exp. June 2021}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Google}{Mountain View, CA}
      {Software Engineering Intern - Play Ads Serving Team}{June 2019 -- Currently}
      \resumeItemListStart
        \resumeItem{Server Front-end}
          {Augmented device to server communication protocol by providing more user context to the server. Device side communication logic was written in Java.}
        \resumeItem{Ads Back-end}
          {Utilized increased context to implement a filter that increased the quality of ads shown and reduced the amount of ads dropped by 19 million a day. New ads server filtering logic was written in C++.}
        \resumeItem{Data Visualization}
          {Sped up team's access to vital monitoring information by reorganizing the navigational structure of dashboards. Made graphs readable by implementing filtering and preprocessing of noisy data.}
        \resumeItem{Launch Stability}
          {Ensured new feature had a stable launch by performing a subset experiment and implementing unit tests and end to end tests. Tests were written in Python.}
        \resumeItem{ML Fairness}
          {Discovered source of machine learning bias in a project and provided feedback on how to resolve it.}
      \resumeItemListEnd

    \resumeSubheading
      {Google}{Mountain View, CA}
      {Engineering Practicum Intern - ChromeOS Team}{June 2018 -- Sep. 2018}
      \resumeItemListStart
        \resumeItem{Linux Build Systems}
          {Updated over 20 packages on ChromeOS and resolved cross-compilation issues.}
        \resumeItem{Data Visualization}
          {Wrote a Python script to automatically create dependency graphs with 1 command.}
        \resumeItem{Open Source}
          {Contributed to the ChromeOS project to prepare for the integration of the FWUPD package.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Davis Labs @ MIT}{Cambridge, MA}
      {Undergraduate Research Assistant}{Dec. 2017 -- June 2018}
      \resumeItemListStart
        \resumeItem{Data Science}
        {Developed software to parse three dimensional mass spectroscopy data.}
        \resumeItem{Data Visualization}
        {Implemented Matplotlib to create graphs and visualize experiment data.}
        \resumeItem{Pyteomics}
        {Utilized Pyteomics library to facilitate the storage and indexing of spectroscopy data.}
      \resumeItemListEnd
      
      \resumeSubheading
      {University of California, Irvine}{Irvine, CA}
      {ASPIRE Team Lead Developer}{July 2016 -- Aug. 2016}
      \resumeItemListStart
        \resumeItem{Project Lead}
          {Led the technical development and fabrication of an infrared controlled Pandora internet radio.}
        \resumeItem{Linux LIRC}
          {Implemented the Linux LIRC libraries to enable remote control interface.}
        \resumeItem{Fabrication Technologies}
          {Utilized computer aided design, laser-cutter, and 3-D printing technologies in UCI's FABWorks Lab to rapidly prototype IOT project.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
      \resumeSubItem{RSML Toolkit}
      {Python library for MMORPG economy data retrieval, analysis, and neural net forecasting. Utilizes Keras to create, train, and
       evaluate a neural net model. Utilizes BeautifulSoup to scrape an online wiki for item price data.
       Preprocesses data through Pandas dataframes.}
    \resumeSubItem{ITD?}
      {Python project demonstrating various machine learning methods for facial recognition in pictures.}
      \resumeSubItem{terminal-stock-ticker}
  	  {Terminal based Python utility that displays real-time stock prices and provides insights on investment returns. Utilizes BeautifulSoup to
  	   scrape for stock quotes. }
    \resumeSubItem{StayHacking}
      {24 hour hackathon focused on immigrant labor equality. Led full-stack development of Glassroots homepage.
       Utilized Bootstrap and Javascript to create interactive and engaging website with one-click workflow.}
    \resumeSubItem{Google CSSI}
      {3 week intensive coding boot-camp on Python, Github, Javascript, HTML, CSS, Google Web APIs, and back-end services like AppEngine and DataStore. Designed and deployed an automatically generated site (vmreyes.info) to showcase photographs and life events. Implementation received a 95\% on performance in Google's Lighthouse benchmark.}
  	

  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Relevant Courses}
  \resumeSubHeadingListStart
    \item{
      Algorithms,
      Computation Structures,
      Programming Fundamentals,
      Microeconomics,
      Multi-variable Calculus,
      Constitutional Law
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
